Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-06 appendix.tex
tex

\subsection{Potential Societal Impact}

@@

\subsection{Limitations of Our Method}

@@

\oo{todo}

%\begin{enumerate}[noitemsep, label={Q{\arabic*}.}]
\begin{enumerate}[noitemsep]
		%
	\item \ul{\it There is only $L_\text{T}(\va, \tilde{\va}, \vp)$ in the ICS
		term.  Is it possible to introduce any other triplet combinations among
		the six samples (\ie, three benign and three adversarial)?}\\
		%
		A: We have tried some other combinations, and they are either not
		effective, or causing negative effects.
		%
		In particular, (1) adding $L_\text{T}(\va, \vp, \vn)$ on top of the
		adversarial training loss
		$L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn})$ can improve
		performance on benign examples, but will drastically reduce model
		robustness;
		%
		(2) $L_\text{T}(\vp, \tilde{\vp}, \va)$ \oo{is duplicated, not necessary.}
		%
		(3) $L_\text{T}(\va, \tilde{\va}, \tilde{\vn})$ no distinct difference.
		%
		(4) $L_\text{T}(\va, \vp, \tilde{\vn})$ leads to better performance
		on benign examples, but drastically reduce robustness.

	\item Gradient in figure 5?

	\item Why not aa~p~ in ICS?
		less adversarial, further.
	\item Have you tried FAT?
	\item What if we mix HM(RM) and HM(SM)?
		works but not good enough.
	\item Another example for the GA pseudo-hardness function family?
		sqaure and sqrt.
	\item Why not ResNet-50?
		ttx and video memory.
	\item fix the anchor like ACT?
		not quite helpful. not necessary.
	\item Why compare in theoretical time cost instead of walltime cost?
		Walltime cost does not precisely indicate the true efficiency
		of a defense method, and may even result in unfair comparison.
		isolate the discrepancy from implementation and engineering tricks,
		as well as software / hardware differences.
	\item full data sheet for tab 2?
		\cref{tab:srcdest}

	\item Details of existing defense methods?

	\item Loss normalization with $u$?

	\item Hardware and software platform?

	\item Complete Table for Sec~4.1 Hardness Selection?

	\item Why not wall time as training cost?

	\item the destination hardness is semihard (or something between semihard
		and softhard, we leave new sampling strategy for future work).

	\item Note, naive combination of benign training and adv train does not lead to better
result, why? mix 0.5

	\item why experiment, 8 step by default

@@

	\item [\xmark] Multicard DDP and single card training leads to different
		performance, regardless of the exact model of GPUs.
		%
		According to the observation, single card training leadss to a lower
		recall performance and a higher robustness score.
		%
		More efficient? This should be ok.
		%
		But be careful when doing ablation studies as this will greatly
		interfere with the conclusions.

@@

	\item [Q] Is ACT equivalent to $HM(H_\mathsf{S},0)$.

@@

	\item [ICS] adversarial training that does not allow embedding move may
		encourage model collapse. Maybe we just apply some loosened restrction
		such as aap? i.e. $(a,\tilde{a},p;\gamma=0)$.

>>>>

\subsection{Potential Societal Impact}
\label{sec:a1}

@@

\subsection{Limitations of Our Method}
\label{sec:a2}

@@

	 fix the anchor like ACT?
		not quite helpful. not necessary.

	 What if we mix HM(RM) and HM(SM)?
		works but not good enough.

	 Note, naive combination of benign training and adv train does not lead to better result, why? mix 0.5

\subsection{Graduate Adversary}

	 Another example for the GA pseudo-hardness function family?
		sqaure and sqrt.

	 Loss normalization with $u$?

\subsection{Intra-Class Structure (ICS)}

	 Gradient in figure 5?

	\ul{\it There is only $L_\text{T}(\va, \tilde{\va}, \vp)$ in the ICS
		term.  Is it possible to introduce any other triplet combinations among
		the six samples (\ie, three benign and three adversarial)?}\\
		%
		A: We have tried some other combinations, and they are either not
		effective, or causing negative effects.
		%
		In particular, (1) adding $L_\text{T}(\va, \vp, \vn)$ on top of the
		adversarial training loss
		$L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn})$ can improve
		performance on benign examples, but will drastically reduce model
		robustness;
		%
		(2) $L_\text{T}(\vp, \tilde{\vp}, \va)$ \oo{is duplicated, not necessary.}
		%
		(3) $L_\text{T}(\va, \tilde{\va}, \tilde{\vn})$ no distinct difference.
		%
		(4) $L_\text{T}(\va, \vp, \tilde{\vn})$ leads to better performance
		on benign examples, but drastically reduce robustness.

	 Why not aa~p~ in ICS?
		less adversarial, further.

	 [ICS] adversarial training that does not allow embedding move may
		encourage model collapse. Maybe we just apply some loosened restrction
		such as aap? i.e. $(a,\tilde{a},p;\gamma=0)$.

\subsection{Empirical Robustness Score (ERS)}

\subsection{Experiment and Evaluation}

	 why experiment, 8 step by default

	 Why not ResNet-50?
		ttx and video memory.

	 Why compare in theoretical time cost instead of walltime cost?
		Walltime cost does not precisely indicate the true efficiency
		of a defense method, and may even result in unfair comparison.
		isolate the discrepancy from implementation and engineering tricks,
		as well as software / hardware differences.

	 Complete Table for Sec~4.1 Hardness Selection?

	 full data sheet for tab 2?
		\cref{tab:srcdest}

	[\xmark] Multicard DDP and single card training leads to different
		performance, regardless of the exact model of GPUs.
		%
		According to the observation, single card training leadss to a lower
		recall performance and a higher robustness score.
		%
		More efficient? This should be ok.
		%
		But be careful when doing ablation studies as this will greatly
		interfere with the conclusions.

\subsection{Potential Future Work}

	 Have you tried FAT?

	 the destination hardness is semihard (or something between semihard
		and softhard, we leave new sampling strategy for future work).

@@

@@

@@
